Discovery of s-process enhanced stars in the LAMOST survey

### 2018-04-15 article/ms.tex
i got git work good

In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements directly using stellar synthesis. Finally, we validate our results using high resolution spectra of a number of candidates. Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only. Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. Most of our barium stars ($69\%$) show strong carbon enhancements, yet, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement. We argue this may have been a selection bias in previous studies. A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.

%The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosyntheic processes that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon and heavy elements (Z > 30) are historically referred to as 'barium stars'.  Here, we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis. Finally, we validate our results using high resolution spectra of a number of candidates. Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only. The unusual chemical abundance patterns of barium stars can be explained if these are in the AGB of stellar evolution. However, many barium stars  have not yet evolved through the red giant phase. Instead, these less evolved 'barium stars' are generally thought to have accreted mass from a more evolved AGB companion.  Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. These less evolved stars are uniquely informative on the binary fraction, AGB yields, mass transfer and stellar evolution. A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star. Most of our barium stars (put in percentage) show strong carbon enhancements, consistent with mass transfer from a low-mass AGB companion. Although, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies. When binary properties become available from end-of-mission Gaia astrometry, our sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.

@@

The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosyntheic processes that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are historically referred to as 'barium stars' as first recognised by \citet{Bidelman1951}. Barium enhanced stars exist as either intrinsic or extrinsic objects, stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars. These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements produced through the slow neutron capture process and exist on the surface as the result of a thermal pulsing cycle. According to the mass-transfer hypothesis, extrinsic barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determined 85\% of all barium stars are in binary systems and claimed that those that appear to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges as detailed by \citet{pourbaix2004}. For these reasons, the properties and occurrence rate of barium stars are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

The s-process, occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}. Late in the AGB phase, during the TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core. These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This phase of expansion and resulting inward movement called the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, surface enrichment in $^{12}$C and heavy elements produced by the s-process, is a result of the repeated inward extensions of TDU \citep[e.g.,][]{busso2001}. The star contracts post dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times, and its frequency is dependent on the initial mass, composition, and mass-loss rate of the star.

Barium giants can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$. The minimum mass for these giants is defined by the mass needed for core helium and carbon burning, which decrease as metallicity decreases. The age of these stars vary considerably, with some as old as $\approx$ 12\,Gyr in metal-poor globular clusters. Metal poor stars enhanced in barium are defined in the literature as CH stars. In contrast, metal-rich, less massive stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}. Furthermore, metal rich stars enhanced in barium are defined in the literature as Bariu stars.

Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, to explore the binary fraction at different metallicities, and then to compare to AGB star yields at different masses and metallicities.
%The relationship between barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 967 s-process candidates. In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis} we discuss the properties of our barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

@@

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}. This data-driven model was used to estimate stellar labels for 454,180 giant stars. We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars. Cross-validation tests shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are comparable to the APOGEE uncertainties \citep{alam2015}.

\subsubsection{Candidate selection} \label{sec:cand}
The barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. Specifically, we identified barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively. A negative residual, as shown in a candidate barium star in Figure \ref{fig:figure1}, illustrates an enhancement in the \ion{Ba}{II} and \ion{Sr}{II} lines at 4554\,\AA\, and 4077\,\AA, respectively. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. Stars identified high levels of barium (and not necessarily strontium) required enhancement in both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars exclusively enhanced in strontium we looked for significant residuals at the 4077\,\AA\ and 4215\,\AA\ absorption lines.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process rich candidates which are provided in Table 1 (online only material) including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 with exclusively strontium enhancement.

For the remainder of this paper we restrict our analysis to the 257 classical `barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.

It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 257 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12. However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement. Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement. $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefor conclude that this single deviant case can be classified as a barium star. Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$. Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.

@@

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 barium stars. We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select barium stars enhanced in sodium, and required significant absorption in both features. Only 5/257 barium stars met this criteria.

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\section{Follow-up observations with Magellan/MIKE}

@@

\subsection{Extrinsic or intrinsic}
Barium enhanced stars exist as either intrinsic or extrinsic objects. Intrinsically enhanced barium stars must be massive enough to reach the TP-AGB phase, and extrinsic barium stars must be in a binary with a previously polluting TP-AGB star companion (AGB S star). Figure \ref{fig:figure2} shows that the majority of our stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, highlighting that all stars in our sample are not evolved enough to have already reached the TP-AGB phase and therefore, must be extrinsic barium stars. Although, it is noted, stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB stars, and their intrinsic or extrinsic nature is not certain. It is noted, in the previous literature \citep{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars). In comparison, we find that all our barium candidates to be extrinsic. This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB barium stars. Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of red giant stars. Given this bias, Figure \ref{fig:figure3} illustrates through the temperature, and log g ranges present, that our sample is entirely populated by red giant extrinsic barium stars. This suggests unaccounted selection biases in previous studies towards luminous AGB S stars.

@@

\subsection{Sodium enhancment}
Sodium overabundances observed in the atmospheres of giants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}. Sodium is transported to the surface of these giants via mixing during the first dredge-up and stars with a  minimum mass of $1.5\,M_\odot$ can exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987,smiljanic2012}. \citet{antipova2004} reported sodium enhancements in 3 of their 16 barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase. Moreover, they suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, however, these [Na/Fe] ratios do not exhibit variations in metallicity. Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

We find that $<2$\,\% of our barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}, indicating all s-process enhanced stars will exhibit Na enhancement. We also note that the 5 sodium-enhanced barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios. It is important to note, sodium enhancement can occur due to the presence of interstellar dust. Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have E(B-V)$\approx$ 0.35, suggesting that the flux residuals around the Na doublet are due to interstellar absorption. However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating, the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 barium candidates, but more importantly, sodium enhancement is by no means ubiquitous in barium stars. However, it should be highlighted that low resolution spectra can result in Na line saturation, limiting the flux enhancement even with an abundance enhancement.

The data that led \citet{decastro2016} to conclude that barium stars have higher [Na/Fe] ratios came from many literature sources. Therefore, it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio. These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic barium stars (by definition) have low $\log{g}$ values. We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample. From our data we conclude that barium stars do not have higher [Na/Fe] abundance ratios on average, and suggest that the effect seen in previous works was due to systematic effects between literature sources.

>>>>

In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements using stellar synthesis. Finally, we take advantage of free observing time, and obtain high resolution spectra of a number of candidates. Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only. Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. Most of our barium stars ($69\%$) show strong carbon enhancements, yet, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement. We argue this may have been a selection bias in previous studies. A comparison with AGB yields suggests the main neutron source responsible for the Ba and Sr enhancements is the $C^{13}(\alpha,n)O^{16}$ reaction chain. Additionally, theoretical models show that this source is dominant in low-mass AGB stars thus, it follows that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.

%that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.

%The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosynthetic processes that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon and heavy elements (Z > 30) are historically referred to as 'barium stars'.  Here, we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis. Finally, we validate our results using high resolution spectra of a number of candidates. Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only. The unusual chemical abundance patterns of barium stars can be explained if these are in the AGB of stellar evolution. However, many barium stars  have not yet evolved through the red giant phase. Instead, these less evolved 'barium stars' are generally thought to have accreted mass from a more evolved AGB companion.  Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. These less evolved stars are uniquely informative on the binary fraction, AGB yields, mass transfer and stellar evolution. A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star. Most of our barium stars (put in percentage) show strong carbon enhancements, consistent with mass transfer from a low-mass AGB companion. Although, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies. When binary properties become available from end-of-mission Gaia astrometry, our sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.

@@

The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosynthetic processes, that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are referred to as 'barium stars' as first recognised by \citet{Bidelman1951}. The naming convention associated with barium stars is historical, it is therefore, for the purposes of this paper, necessary to classify definitions used for subsequent discussions. Barium enhanced stars exist as either extrinsic or intrinsic objects, extrinsic barium stars are stellar phenomena exhibiting s-process element enhancement as the result of some polluting process. Stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars. These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase. During this stage of nucleosynthesis, this is an overabundance of both carbon and heavy elements produced through the slow neutron capture process, and exist on the surface as the result of a thermal pulsing cycle. According to the mass-transfer hypothesis, extrinsic barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}. Both dynamical systems require a binary configuration a previous TP-AGB companion star (AGB S star), in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determined 85\% of all barium stars exist within binary systems. They further claimed that stellar objects which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations, only occurring in a small ranges as detailed by \citet{pourbaix2004}. For these reasons, the properties and occurrence rate of barium stars are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

The s-process, occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}. Late in the AGB phase, during the TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core. These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, surface enrichment in $^{12}$C and heavy elements produced by the s-process, is a result of the repeated inward extensions of TDU \citep[e.g.,][]{busso2001}. The star contracts post dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times, and its frequency is dependent on the initial mass, composition, and mass-loss rate of the star.

Barium giants can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$. The minimum mass for these giants is defined by the mass needed for core helium and carbon burning, which decrease as metallicity decreases. The age of these stars vary considerably, with some as old as $\approx$ 12\,Gyr in metal-poor globular clusters. Metal poor stars enhanced in barium are defined in the literature as CH stars. In contrast, metal-rich, less massive stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}. Furthermore, metal rich stars enhanced in barium are defined in the literature classically as barium stars.

Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to: compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.
%The relationship between barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 967 s-process candidates. In Section \ref{sec:methods}, we describe the observations and candidate selection. Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis}, we discuss the properties of our barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

@@

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model, and constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}. This data-driven model was used to estimate stellar labels for 454,180 giant stars. We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars. Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are comparable to the APOGEE uncertainties \citep{alam2015}.

\subsubsection{Candidate selection} \label{sec:cand}
The barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as a disparity between the normalised LAMOST flux and the data driven model, \emph{The Cannon}, derived by \citet{ho2017}. Specifically, we identified barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively. A negative residual, as shown in a candidate barium star in Figure \ref{fig:figure1}, illustrates an enhancement in the \ion{Ba}{II} and \ion{Sr}{II} lines at 4554\,\AA\, and 4077\,\AA, respectively. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements, given a well-fit model for the data. Stars identified high levels of barium (and not necessarily strontium) required enhancement in both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars exclusively enhanced in strontium we looked for significant residuals at the 4077\,\AA\ and 4215\,\AA\ absorption lines.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process rich candidates which are provided in Table 1, for which a portion is shown to demonstrate its style and content, it's available online in its entirety. This stellar sample consists of; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 with exclusively strontium enhancement.

For the remainder of this paper we restrict our analysis to the 257 classical `barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bona fide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.

It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 257 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12. However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement. Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement. $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefore conclude that this single deviant case can be classified as a barium star. Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$. Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.

@@

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 barium stars. We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features. Only 5/257 barium stars met this criteria.

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum. We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at the single technetium line 4238\,\AA, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 (available online in its entirety) nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\section{Follow-up observations with Magellan/MIKE} \label{sec:observations}

@@

\subsection{Extrinsic or intrinsic}
Barium enhanced stars exist as either intrinsic or extrinsic stellar objects. Intrinsically enhanced barium stars must be massive enough to reach the TP-AGB phase, and extrinsic barium stars must be in a binary with a previously polluting TP-AGB star companion (AGB S star). Figure \ref{fig:figure2} shows that the majority of our stellar sample exists within temperature and luminosity ranges not enveloped by the AGB. This highlights that our sample does not contain stars to the degree of evolution required to reach the TP-AGB phase, and therefore, must be extrinsic barium stars. However, stars with temperatures below 3800K in Figure \ref{fig:figure2} are potential AGB stars, and their intrinsic or extrinsic nature is not certain. Additionally, it's important to note, previous literature \citep{van2017}, state only 33\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars). In comparison, we find that all our barium candidates to be extrinsic. This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous AGB S stars. Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of red giant stars. Given this bias, Figure \ref{fig:figure3} illustrates through the temperature, and log g ranges present, that our sample is exclusively populated by red giant extrinsic barium stars. This suggests unaccounted selection biases in previous studies towards luminous AGB S stars.

@@

\subsection{Sodium enhancement}
Sodium overabundances observed in the atmospheres of giants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}. Sodium is transported to the surface of these giants via mixing during the first dredge-up, and stars with a  minimum mass of $1.5\,M_\odot$ can exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987,smiljanic2012}. \citet{antipova2004} reported sodium enhancements in 3 of their 16 barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase. Moreover, they suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, however, these [Na/Fe] ratios do not exhibit variations in metallicity. Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

We find that $<2$\,\% of our barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}, indicating all s-process enhanced stars will exhibit Na enhancement. We also note that the 5 sodium-enhanced barium stars all have values of, $\log{g} \approx 3$, which is inconsistent with the literature. Previous studies suggest, lower $\log{g}$ values are expected, given low $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios. It is important to note, sodium enhancement can occur due to the presence of interstellar dust. Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have E(B-V)$\approx$ 0.35, suggesting that the flux residuals around the Na doublet are due to interstellar absorption. However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating, the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 barium candidates, but more importantly, sodium enhancement is by no means ubiquitous in barium stars. However, it should be highlighted that low resolution spectra can result in Na line saturation, limiting the flux enhancement even with an abundance enhancement.

The data that led \citet{decastro2016} to conclude that barium stars have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on barium stars. This has the potential to contain unresolved differences in the reported [Na/Fe] abundance ratio. These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic barium stars (by definition) have low $\log{g}$ values. We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample, and we conclude that barium stars do not have higher [Na/Fe] abundance ratios on average.
